Naturalness in U(1) extensions of the MSSM

### 2014-12-17 paper/e6ssm-tuning-paper.tex
Added details of what is fixed for stop scans

In Fig. \ref{} we fix blah blah bah [Dylan insert details please] and
show how fine tuning varies as we increase the stop masses. However
thius tuning inly really becomes large for very large stop masses.  On
the other hand if cuttoff is increased then stop masses of severalk
TeV can result in tuning of [insert] as shown in Fig.~\ref{}.

>>>>

To illustrate this, in Fig. \ref{} we show the variation in fine tuning when we fix $\mu=-97$ GeV and $B=-85$ GeV, 
and scan over the stop masses and mixing, with $500 \textrm{ GeV} \leq m_{Q_3},m_{u_3}\leq 10\textrm{ TeV}$ and $-3810\textrm{ GeV}\leq A_t\leq -20\textrm{ GeV}$, for $M_X=20$ TeV, $50$ TeV and $100$ TeV. 
However
thius tuning inly really becomes large for very large stop masses.  On
the other hand if cuttoff is increased then stop masses of severalk
TeV can result in tuning of [insert] as shown in Fig.~\ref{}.\\ \\
